\cvsection{Work Experience}

\begin{cventries}

	\cventry
	{Software Architect, Software Engineer}
	{\href{https://www.linkedin.com/company/klarna/}{Klarna}}
	{\href{https://www.google.com/maps/place/Stockholm}{Stockholm, Sweden}}
	{Apr 2022 - Present}
	{
		\begin{cvitems}
			\item {Developed credit card-focused products.}
			\item {Integrated APIs, compliance, and reporting systems with  \href{https://www.linkedin.com/company/visa/}{Visa}.}
			\item {Coordinated development planning across multiple teams and departments.}
			\item {Contributed to the growth and development of the internal \href{https://en.wikipedia.org/wiki/Scala_(programming_language)}{Scala} community and ecosystem.}
		\end{cvitems}
	}


	\cventry
	{Software Architect, Software Engineer}
	{\href{https://www.linkedin.com/company/dsr-corporation/}{DSR Corporation}}
	{\href{https://www.google.com/maps/place/Voronezh,+Voronezh+Oblast,+Russia}{Voronezh, Russian Federation}}
	{Oct. 2019 - Apr, 2022}
	{
		\begin{cvitems}
			\item {Led the migration of petabytes of data from legacy \href{https://en.wikipedia.org/wiki/Hierarchical_storage_management}{HSM} to modern cloud infrastructure.}
			\item {Developed a JVM-based autonomous service to facilitate seamless data transfer and management during the migration process.}
			\item {Designed and implemented an on-premise development pipeline for the service, ensuring seamless deployment and operation within the organization's infrastructure.}
		\end{cvitems}
	}

	\cventry
	{Theoretical Physics Lab Assistant}
	{\href{https://www.linkedin.com/school/\%D0\%B2\%D0\%BE\%D1\%80\%D0\%BE\%D0\%BD\%D0\%B5\%D0\%B6\%D1\%81\%D0\%BA\%D0\%B8\%D0\%B9-\%D0\%B3\%D0\%BE\%D1\%81\%D1\%83\%D0\%B4\%D0\%B0\%D1\%80\%D1\%81\%D1\%82\%D0\%B2\%D0\%B5\%D0\%BD\%D0\%BD\%D1\%8B\%D0\%B9-\%D1\%83\%D0\%BD\%D0\%B8\%D0\%B2\%D0\%B5\%D1\%80\%D1\%81\%D0\%B8\%D1\%82\%D0\%B5\%D1\%82}{Voronezh State University}}
	{\href{https://www.google.com/maps/place/Voronezh,+Voronezh+Oblast,+Russia}{Voronezh, Russian Federation}}
	{Jan. 2019 - Oct. 2019}
	{
		\begin{cvitems}
			\item {Developed computational programs to support research on \href{https://journals.aps.org/pra/abstract/10.1103/PhysRevA.106.033117}{``Coulomb effects in the high-energy part of above-threshold-ionization spectra in intense bicircular laser fields``}.}
			\item {Applied \href{https://en.wikipedia.org/wiki/Functional_analysis}{functional analysis} techniques to enhance the mathematical rigor of theoretical physics research.}
		\end{cvitems}
	}

\end{cventries}
